Adaptive Global Optimization Using Graphics Accelerators

### 2020-09-25 2020/RSD_GPU/RSD2020.tex
fix comments from program commettee

\begin{document}
\mainmatter              % start of a contribution
%
\title{Adaptive global optimization using graphics accelerators\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
%
\titlerunning{Adaptive global optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{
Konstantin A. Barkalov%(ORCID 0000-0001-5273-2471)
$^1$ \and
Ilya G. Lebedev \letter%(ORCID 0000-0002-8736-0652)
$^1$ \and 
Vassili V. Toropov%(ORCID 0000-0002-7017-5055)
$^{1,2}$
}

%
\authorrunning{K.A. Barkalov \and I.G. Lebedev \and V.V. Toropov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Konstantin Barkalov and Ilya Lebedev }
%

@@

\section{Multidimensional parallel global search algorithm}\label{Sec_GSA}
Let's consider the problem of finding the global minimum of the \(N\)-dimensional function \(\varphi(y)\) in the hyperinterval  \(D=\{y\in R^N:a_i\leqslant x_i\leqslant{b_i}, 1\leqslant{i}\leqslant{N}\}\).  We will assume that the function satisfies the Lipschitz condition with an a priori unknown constant \(L\).
\begin{equation}
\label{task}
\varphi(y^*)=\min\{\varphi(y):y\in D\},
\end{equation}
\begin{equation}
\label{lip}
|\varphi(y_1)-\varphi(y_2)|\leqslant L\Vert y_1-y_2\Vert,y_1,y_2\in D,0<L<\infty.
\end{equation}

@@

\section{Dimensionality reduction schemes in global optimization problems}

\subsection{Dimensionality reduction using multiple mappings}

@@

\subsection{Recursive dimensionality reduction scheme}

@@

\subsection{Adaptive dimensionality reduction scheme}

@@

\section{GPU implementation}

\subsection{General scheme}

@@

\subsection{Organization of parallel computing}

@@

\section{Numerical experiments}

>>>>

\begin{document}
\mainmatter              % start of a contribution
%
\title{Adaptive Global Optimization Using Graphics Accelerators
%\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
%
\titlerunning{Adaptive Global Optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{
Konstantin Barkalov%(ORCID 0000-0001-5273-2471)
$^1$ \and
Ilya Lebedev \letter%(ORCID 0000-0002-8736-0652)
$^1$ \and 
Vassili Toropov%(ORCID 0000-0002-7017-5055)
$^{1,2}$
}

%
\authorrunning{K. Barkalov \and I. Lebedev \and V. Toropov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Konstantin Barkalov and Ilya Lebedev }
%

@@

\section{Multidimensional Parallel Global Search Algorithm}\label{Sec_GSA}
Let's consider the problem of finding the global minimum of the \(N\)-dimensional function \(\varphi(y)\) in the hyperinterval  \(D=\{y\in R^N:a_i\leqslant x_i\leqslant{b_i}, 1\leqslant{i}\leqslant{N}\}\).  We will assume that the function satisfies the Lipschitz condition with an a priori unknown constant \(L\).
\begin{equation}
\label{task}
\varphi(y^*)=\min\{\varphi(y):y\in D\},
\end{equation}
\begin{equation}
\label{lip}
|\varphi(y_1)-\varphi(y_2)|\leqslant L\Vert y_1-y_2\Vert,y_1,y_2\in D,0<L<\infty.
\end{equation}

@@

\section{Dimensionality Reduction Schemes in Global Optimization Problems}

\subsection{Dimensionality Reduction Using Multiple Mappings}

@@

\subsection{Recursive Dimensionality Reduction Scheme}

@@

\subsection{Adaptive Dimensionality Reduction Scheme}

@@

\section{GPU Implementation}

\subsection{General Scheme}

@@

\subsection{Organization of Parallel Computing}

@@

\section{Numerical Experiments}
